---
title: "COVID-19: Epidemic curves, by city or country"
author: "Simon Thornley, University of Auckland."
date:  "`r format(Sys.time(), '%e %B, %Y')`"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("main.R")

```


## Daily incident confirmed cases.

This is generated from the [Johns Hopkins University github website](https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Confirmed.csv), which is a tally of cumulative cases by city or country. The plots displayed here, in contrast, show the daily incidence or count of newly diagnosed cases. Plots of cumulative cases can only increase (or at best flatten off). For a more accurate indication of the extent of the epidemic, these plots show areas where incidence is increasing or declining. In comparison, coronavirus cases are actually declining in some centres, particularly from cities within China. 

There are, of course, questions about how accurate these data are and how extensively potential cases are screened.

The plots are sorted with the city or country with the highest mean daily count over the last week. The red line is a loess smoother (type of moving average) that indicates the average overall trend (for some plots it may fall over and just connect the dots). Plots of daily mortality counts are available [here](https://sithor.shinyapps.io/coronavirus_mortality/).

```{r plots_by_city, echo = FALSE}
for (i in 1:length(x)) {
  plot_and_lowess(country = names(x)[i])
}



```
